1. Row Node.js project = exam
2. multer project // express-fileupload  
   =>  Amit data (GitHup link => https://github.com/amitbd599/express-fileupload-project/blob/main/app/service/FileService.js)

   => sumit Shah (youtube video)

3. Row MongoDB project => CRUD operations
4. module-17 project => CRUD + Profile + Tasks project

8. Refesher Module-20 => 7 project
9. login-registration-passowrd-reset-profile-3
10. payment-getway-impletion-4 
11. Product Cart List API Project-5 Refesher-module-1 
12. yarn-install-8
13. Blog with Comments join API Project-6
14. express.js project structure-2
15. express-fileupload-project-7

.......................................................
16. Module-21-exam => Assignment
16. Module-21-exam => Database Image upload save
16. Module-21-exam => Live Test Exam
.........................................................

17. Module-16 Pre-record-video-38

5. 18 pre-record video project //  18 pre-record video live project
6. 18 -19 live project => 18-2live video // 19-live video => Live video project

7. Module-19 Catch-Log-Errors-Express.js-Middleware
8. module-18 => Securing Express.js APIs with JWT Authentication and Sending Emails using NodeMailer 


////////////////////////////////////////////////////////////////////////////////////////
***** md5 // becrypt passowrd securety storng.
**** passowrd validation code UserModel
**** Phone number validation code UserModel

//////////////////////////////////////////////////////////////////////////////////////////